
\documentclass[12pt]{article}     
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage[top=2.5cm, bottom=2.5cm, left=3cm, right=3cm]{geometry}
\usepackage{titlesec}
\usepackage{longtable}
\usepackage[table,xcdraw]{xcolor}
\usepackage{todonotes}
\usepackage{float}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{csquotes}
\usepackage{tocloft}
\usepackage{amssymb}
\renewcommand{\labelitemi}{\tiny$\blacksquare$} %For square itemized lists
\usepackage{caption} 
\captionsetup{labelsep=period}
\usepackage{verbatimbox} %To put program code in the center using Verbatim
\titlelabel{\thetitle.\quad}
\usepackage{times}
\usepackage{fancyhdr}
\setlength{\parindent}{0cm}
\usepackage{setspace}
\onehalfspacing
\setlength{\parskip}{\baselineskip}
\usepackage{amsmath} 
\usepackage{amsthm}
% Packages for building tables and tabulars 
\usepackage{array}
\usepackage{tabu}   % Wide lines in tables
\usepackage{xspace} % Non-eatable spaces in macros
\usepackage[colorlinks=true,linkcolor=blue]{hyperref}
\usepackage[all]{hypcap}
\usepackage{url}
% Packages for defining colourful text together with some colours
%\usepackage[table,xcdraw]{xcolor}
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
\definecolor{lightblue}{rgb}{0.95,0.97,1.0}
\definecolor{darkblue}{rgb}{0.90,0.92,1.0}
\usepackage{color}

% Standard package for drawing algorithms
% Since the thesis in article format we must define \chapter for
% the package algorithm2e (otherwise obscure errors occur) 
\let\chapter\section
\usepackage{algorithm2e}

% Macros that make sure that the math mode is set
\newcommand{\typeF}[1] {\ensuremath{\mathsf{type_{#1}}}\xspace}
\newcommand{\opDiv}{\ensuremath{\backslash \mathsf{div}}\xspace} 
\usepackage{listings}

\lstset{ 
  %language=python,                % the language of the code
  language=C++,
  basicstyle=\footnotesize,        % the size of the fonts that are used for the code
  %numbers=left,                   % where to put the line-numbers
  %numberstyle=\footnotesize,      % the size of the fonts that are used for the line-numbers
  numberstyle=\tiny\color{gray}, 
  stepnumber=1,                    % the step between two line-numbers. If it's 1, each line 
                                   % will be numbered
  numbersep=5pt,                   % how far the line-numbers are from the code
  backgroundcolor=\color{white},   % choose the background color. You must add \usepackage{color}
  showspaces=false,                % show spaces adding particular underscores
  showstringspaces=false,          % underline spaces within strings
  showtabs=false,                  % show tabs within strings adding particular underscores
  frame = lines,
  %frame=single,                   % adds a frame around the code
  rulecolor=\color{black},		   % if not set, the frame-color may be changed on line-breaks within 
                                   % not-black text (e.g. commens (green here))
  tabsize=2,                       % sets default tabsize to 2 spaces
  captionpos=b,                    % sets the caption-position to bottom
  breaklines=true,                 % sets automatic line breaking
  breakatwhitespace=false,         % sets if automatic breaks should only happen at whitespace
  %title=\lstname,                 % show the filename of files included with \lstinputlisting;
                                   % also try caption instead of title
                                   % also try caption instead of title
  keywordstyle=\color{blue},       % keyword style
  commentstyle=\color{dkgreen},    % comment style
  stringstyle=\color{mauve},       % string literal style
  escapeinside={\%*}{*)},          % if you want to add a comment within your code
  morekeywords={*,game, fun}       % if you want to add more keywords to the set
}

\usepackage{multirow}
\setlength{\tabcolsep}{0pt}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1-\arrayrulewidth\relax}}
\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1-\arrayrulewidth\relax}}

\usepackage{booktabs,fixltx2e}
\usepackage{tikz}
%used for ex. for m prime
\usepackage{flexisym}
\usepackage{footnote}

\usepackage{arydshln}
\usepackage{placeins}
\usepackage{enumitem}
\usepackage{cleveref}
\crefformat{footnote}{#2\footnotemark[#1]#3}
\usepackage{IEEEtrantools}

\begin{document}
\bstctlcite{IEEEexample:BSTcontrol}
%------------------------------TIITELLEHT---------------------------------
\thispagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\headheight = 57pt
\footskip = 11pt
\headsep = 0pt

\chead{
 \textsc{\begin{Large} %Tekst suurtähtedega ja suuremaks
	Tallinn University of Technology\\
	\end{Large} }
	Department of Computer Science\\	
	TUT Center for Digital Forensics and Cyber Security
}
\vspace*{7 cm}

\begin{center}
ITC70LT\\[0cm]

Gvantsa Grigolia 144965\\
\vspace{15pt}
\begin{LARGE}
\textsc{Evaluation of data ownership solutions in remote storage.\\}
\end{LARGE}
\vspace{10pt}
Master Thesis\\[2cm]
\end{center}

\begin{flushright}
Supervisor: Ahto Buldas\\[0cm]
Professor \\[0cm]
\end{flushright}

\cfoot{Tallinn 2016} 
\pagebreak

%---------------------------AUTORIDEKLARATSIOON-------------------------
\section*{\begin{center}
 Autorideklaratsioon
\end{center}}


Autorideklaratsioon on iga lõputöö kohustuslik osa, mis järgneb tiitellehele.
Autorideklaratsioon esitatakse järgmise tekstina:

Olen koostanud antud töö iseseisvalt. Kõik töö koostamisel kasutatud teiste autorite tööd, olulised seisukohad, kirjandusallikatest ja mujalt pärinevad andmed on viidatud. Käsolevat tööd ei ole varem esitatud kaitsmisele kusagil mujal.

Autor: [Ees$-$ ja perenimi]

[\today]
\pagebreak

%---------------------------ANNOTATION---------------------------------
\section*{\begin{center}
Annotatsioon
\end{center}}

Annotatsioon on lõputöö kohustuslik osa, mis annab lugejale ülevaate töö eesmärkidest, olulisematest käsitletud probleemidest ning tähtsamatest tulemustest ja järeldustest. Annotatsioon on töö lühitutvustus, mis ei selgita ega põhjenda midagi, küll aga kajastab piisavalt töö sisu. Inglisekeelset annotatsiooni nimetatakse Abstract, venekeelset aga


Sõltuvalt töö põhikeelest, esitatakse töös järgmised annotatsioonid:
\begin{itemize}
\item kui töö põhikeel on eesti keel, siis esitatakse annotatsioon eesti keeles mahuga $\frac{1}{2	}$ A4 lehekülge ja annotatsioon \textit{Abstract} inglise keeles mahuga vähemalt 1 A4 lehekülg;
\item kui töö põhikeel on inglise keel, siis esitatakse annotatsioon (Abstract)  inglise keeles mahuga $\frac{1}{2}$ A4 lehekülge ja annotatsioon eesti keeles mahuga vähemalt 1 A4 lehekülg;
\end{itemize}

Annotatsiooni viimane lõik on kohustuslik ja omab järgmist sõnastust:

Lõputöö on kirjutatud [mis keeles] keeles ning sisaldab teksti [lehekülgede arv] leheküljel, [peatükkide arv] peatükki, [jooniste arv] joonist, [tabelite arv] tabelit.
\pagebreak


%-----------------------------ABSTRACT-----------------------------------

\section*{\begin{center}
Abstract
\end{center}}
Võõrkeelse annotatsiooni koostamise ja vormistamise tingimused on esitatud eestikeelse annotatsiooni juures.

The thesis is in [language] and contains [pages] pages of text, [chapters] chapters, [figures] figures, [tables] tables.
\pagebreak

%---------------------Glossary of terms and Abbreviations---------------------

%\section*{\begin{center}
%Glossary of Terms and Abbreviations
%\end{center}}
%Lühendite  ning  mõistete  sõnastikku  lisatakse kõik töö põhitekstis kasutatud  uued  ning  ka mitmetähenduslikud üldtuntud terminid. Näiteks inglisekeelne lühend PC  võib tähendada nii Personal Computer kui ka Program Counter, sõltuvalt kontekstist. Lühendid ja mõisted esitatakse tabuleeritult kahte tulpa selliselt, et vasakul on esitatud lühend või mõiste ja paremal tulbas seletus. Inglisekeelsed sõnad seletustes esitatakse kaldkirjas. Alltoodud näited esitavad lühendite ja mõistete sõnastiku korrektset vormistamist.

%\begin{tabular}{p{3 cm}ll}
%IPv6&Internet Protocol version 6\\
%ICMPv6&Internet Control Message Protocol version 6\\
%Node&ll\\
%NAT&dd\\
%IANA&Internet Assigned Numbers Authority\\
%BYID&Bring Your Own Device\\
%OS&Operating System\\
%IoT&Internet of Things\\
%rootkit&ff
%\end{tabular}
%\pagebreak

\tableofcontents
\newpage
\listoffigures
\pagebreak
\listoftables
\pagebreak

\section{Introduction}
\label{sec:1}

Describes the problem statement, illustrates why this is a problem and describes the contribution the thesis makes in solving this problem. Optionally, 
it can give a short description (1-3 sentences each) of the remaining chapters. Good introductions are concise, typically no longer than 4 pages.\\
%The introduction reveals the full (but summarized) results of your work. This appears counter-intuitive: does this not break the tension, 
%like revealing the name of the murderer on the first page of a thriller? Yes, it does. That is the whole point. A thesis, and thus its architecture, 
%aims primarily to inform, not entertain.

\pagebreak
%---------------------------------TERMS AND DEFINITION -----------------------------------------
\section{Terms and definition}
\label{sec:2}
Defines the fundamental concepts your thesis builds on. Your thesis implements a new type of parser generator and uses the term non-terminal symbol a lot? 
Here is where you define what you mean by it. The key to this chapter is to keep it very, very short. 
Whenever you can, don’t reinvent a description for an established concept, but reference a text book or paper instead.
\pagebreak
%------------------------------BACKGROUND AND RELATED WORK-----------------------------------
\section{Background and Related Work}
\label{sec:3}
%4 -5 pages 
\subsection{Data Deduplication}
\label{sub:Deduplication}
Cloud computing is an on-demand service. Customers are charged based on used storage and bandwidth.\footnote{"With Amazon S3, you pay only for the storage you actually use. There is no minimum fee and no setup cost. Amazon S3 has three pricing components: storage (per GB per month), data transfer in or out (per GB per month), and requests (per n thousand requests per month)." \url{http://aws.amazon.com/s3/pricing/}} Both service providers and customers are interested in cost efficient solutions of cloud storage. Data deduplication offers disk and bandwidth savings. Idea is simple -- avoid or remove a duplicated data. 
This section covers basic concepts of deduplication technology. Lists various methods and processing type sand underlines the approaches used in cloud storage.

\subsubsection{Hash Based Deduplication}
\label{subsub:HashBased}
To remove or avoid duplicated data, it must be detected first. Hash based data deduplication uses the hash values of a file (or data chunk) as a file (or data chunk) identifier. Hashes of files are calculated and then are kept on the server. When the file is uploaded first time, its hash is computed and it is compared with the existing hashes on the server. If there is a match, the file is not stored on the disk (or in case of client-side deduplication, is not transfered at all). Instead, server creates the reference, which points on the already existing file, with the same hash value. If computed hash does not match with any of the hashes, the file together with the hash value is stored on the server.\cite{DeDupOverView}

\subsubsection{Types of Deduplication}
\label{subsub:TypesOfDedup}
Data deduplication differs based on processing methods. If it takes place before the client application transfers the file to the server, it is known as client-side deduplication. If it takes place, after the file is uploaded on server, it is known as server side deduplication. In client-side deduplication scenario, the client application computes the hash of the file and sends it to the server. If the hash already exists on the server side, client application does not send the file. If no match is found, it means,that the file is unique and client application transfers it to the server. On the other hand, if client application directly sends file to the server and server computes the hash after it, it is called server-side deduplication. Both processing methods save storage, but client-side deduplication also reduces bandwidth consumption.\cite{DeDupMethods}\\\\
Apart of divers processing methods, data deduplication differs in processing levels. There are file  and block level data deduplication. Difference between them is intuitive. In case of file level, hash of file is calculated and as a result server stores unique files. In block level scenario, files are divided into blocks(fixed or variable size). Hashes of these blocks are calculated and duplicated data on block level is avoided. \cite{DeDupMethods}\\\\
The last concept is, single and cross client data deduplication. Single client data deduplication removes duplicated data  in scope of one user. Duplicated data will be stored on the server, if it belongs to different users. On the other hand, cross client deduplication vanishes the user boundaries and unique data would be shared among the users.\cite{DeDupMethods}

\subsubsection{Summary}
Cloud storage providers are looking for, the most efficient way to reduce the cost. In cross user client-side deduplication  case, file or ”chunks” of file are stored only ones on the disk and users are sharing the data. It reduces the bandwidth cost dramatically, because the deduplication takes palace on client side, and duplicated files are not uploaded at all.\cite{DeDupDropBox} Such cost reductions is attractive for cloud storage providers, but this technology has some security drawbacks. \hyperref[sub:potentialAttacks]{Next section} covers potential attacks taking place during cross-user client-side data deduplication in cloud storage.


\subsection{Confidentiality and Privacy Issues in Remote Storage}
\label{sub:potentialAttacks}
%$f$
Although deduplication is a beneficial technology, there are security drawbacks, leading to potential attacks. Taking into consideration the behavior of the cross-user client-side data deduplication, it is easy to learn some general facts. This section focuses on attacks breaching the confidentiality of data and privacy of remote storage customers, when cross-user client-side data deduplication takes place.

\subsubsection{Potential Attacks}
Danny Harnik was first who has demonstrated, the potential attacks in remote storage related to data deduplication technology.\cite{Harnik} The paper covers three cases: file detection, file content detection and covert channel. The first case shows, how  trivial is  to learn whether the remote server already contains the particular file or not. Attacker uploads the file and observes the network traffic or the time required to upload the file. If the file already is stored on the server, there is no need to upload it again. Client application sends only the 
hash of the file to the server. The observer detects, that amount of data is smaller then file's size itself(Size of the hash depends on hash function and is smaller then file size). If file is "big enough", observing the time required to upload file on server, is sufficient to learn, whether the server already contains the file or not. The law enforcement authorities, can use this behavior. Check if storage provider contains the file (e.g. file's content is against the law) and later, they can force remote storage service providers to revile the identity of the file owner.\\\\
Data deduplication technology opens the possibility to guess the content of user's data.The approach is straightforward, attacker just tries all possible variations and waits for occurrence of data deduplication. Once it takes place, attacker learns that such file (file with this content) exist on the server. The trick is that, unlike the dictionary attacks it is not detectable. It is the legitimate way to upload new documents on the server.\cite{Harnik} This type of attack is easy to lunch against the files with small min-entropy. To have batter understanding, refer to the following example. Bob is invited at the event in the cinema. He stores his invitation ticket in the cloud. Alice wants to learn the row and the place of Bob's ticket. She put the Bob's name on the right place and  starts to brute force row and place numbers. Alice generates files with different content and uploads on cloud. Once the deduplication takes place, she will get the desired information.\\\\
Last case describes the covert channel. Precondition for this scenario is, that attacker already have to own the victims machine. In order to exchange one bit information "0" or "1", attacker generates two random files  and uploads one of them. If the first file is uploaded the covert channel transfers "0" else it transfers "1" bit. Covert channel can transfers more information, by altering  the number of files or the meaning of file.\cite{Harnik}\\\\
All above stated attacks demonstrates the side channel effects of data deduplication. Attackers exploit the vulnerability, that data deduplication is detectable. But later Halevi states that main issue is not the detectability, but using the hash value as a proxy in remote storage.\cite{PoW} He claims that, to use a hash as a proxy to retrieve the file is vulnerable. Owning a small static piece of the file(e.g. hash of the file) does not necessarily mean owning the entire file. He referees to the Dropship\footnote{\url{https://github.com/driverdan/dropship} - "Instantly transfer files between Dropbox accounts using only their hashes"} open source project, as a brief example of misusing the storage provider. Dropship turn the remote storage  provider into CDN (Content Distribution Network) service. For that time Dropbox\footnote{\url{https://www.dropbox.com/}} was operating based on the cross-user client-side deduplication. The users of Dropship, where able to download the file in their folder, just sending the file’s hash for check to the Server. This open source project was considered as the violation of Terms of Service of the company and is not operating anymore. Halevi introduces the Proof of Ownership Protocol, which dramatically reduces the probability of the attacker to retrieve the file, without owning it. \hyperref[sec:4]{Next section} covers the detail description of Proof of Ownership Protocol and other solutions offered to substitute the hash as a proxy approach for data ownership in remote storage.
%Collects descriptions of existing work that is related to your work. Related, in this sense, means aims to solve the same problem or uses the same approach to solve a different problem. 
%This chapter typically reads like a structured list. Each list item summarizes a piece of work (typically a research paper) briefly and explains the relation to your work. 
%This last part is absolutely crucial: the reader should not have to figure out the relation himself.
%Is your piece better from some perspective? More generalizable? More performant? Simpler? It is ok if it is not, but I want you to tell me.

\subsection{Summary}
The amount of savings offered by data deduplication, depends on data type and content produced by users of such services.\cite{ratio}  In case of office workers as users in remote storage, the benefit from deduplication is high. Office workers use mostly identical template to generate the data and the portion of duplication is high. Applying data deduplication technology saves bandwidth and disk space.  But same time it rises privacy and confidentiality issues. The major weakness is that, client-side deduplication is detectable and using hash as a proof of ownership is not sufficient. Anyone who possesses the hash value of file, is able to retrieve the file from the server.  If the attacker  obtains the hash of the file, he can retrieve the file from the server and gain unauthorized access to it.\\\\
Data privacy issue in cloud computing is one of the aspects that could break the trust of the users towards the service providers. So those who what to stay on the market, should build the systems, which takes into consideration privacy and confidentiality.

\pagebreak

%------------------------------APPROACH-----------------------------------
\section{Approach}
\label{sec:4}

%Outlines the main thing your thesis does. Your thesis describes a novel algorith for X? Your main contribution is a case study that replicates Y? Describe it here.
\begin{itemize}
 \item Proofs of Ownership in Remote Storage Systems - 2011
 \item Boosting Efficiency and Security in Proof of Ownership for Deduplication - 2012
 \item Provable Ownership of File in De-duplication Cloud Storage - 2013
 \item A Secure Client Side Deduplication Scheme in Cloud Storage Environments - 2014
 \item A Tunable Proof of Ownership Scheme for Deduplication Using Bloom Filters - 2014
 \item An efficient confidentiality-preserving Proof of Ownership for Deduplication -2014


\end{itemize}





\pagebreak

%------------------------------EVALUATION-----------------------------------
\section{Evaluation}
\label{sec:5}
Demonstrate why the developed framework  is secure and efficient. 


\begin{enumerate}
 \item Time complexity evaluation.
 \item Cost analyses. 
\end{enumerate}



%Describes why your approach really solves the problem it claims to solve. You implemented a novel algorithm for X? 
%This chapter describes how you ran it on a dataset and reports the results you measured. You replicated a study? This chapter gives the results and your interpretations.

%The Appraoch and Evaluation chapters contain the meat of your thesis. Often, they make up half or more of the pages of the entire document.

\pagebreak

%------------------------------FUTURE WORK-----------------------------------
\section{Future Work}
\label{sec:6}

 In science folklore, the merit of a research question is compounded by the number of interesting follow-up research questions it raises. 
 So to show the merit of the problem you worked on, you list these questions here.
 %If you don’t care about research folklore (I did not as a student),
 %this chapter is still useful: whenever you stumble across something that you should do if you had unlimited time, but cannot do since you don’t, you describe it here. 
 %Typical candidates are evaluation on more study objects, investigation of potential threats to validity, … 
 %The point here is to inform the reader (and your supervisor) that you were aware of these limitatons. Limit this chapter to very few pages. 
 %Two is entirely fine, even for a Master’s thesis.
\pagebreak


%------------------------------CONCLUSIONS-----------------------------------
\section{Conclusions}
\label{sec:7}
Short summary of the contribution and its implications. The goal is to drive home the result of your thesis.
Do not repeat all the stuff you have written in other parts of the thesis in detail. Again, limit this chapter to very few pages. 
The shorter, the easier it is to keep consistent with the parts it summarizes.

\pagebreak

%------------------------------REFERENCES-----------------------------------

\addcontentsline{toc}{section}{References}


\bibliographystyle{IEEEtran}
\bibliography{bibi.bib}


\pagebreak

%-----------------------------APPENDIX--------------------------------

\appendix

\section{Appendix 1}




\end{document}
